\section{Experimental Evaluation}\label{Se:experiments}

In this section, we describe the \Tool\ implementation, and present two sets of experiments that we have conducted to evaluate our approach.

\subsection{The \Tool\ System}\label{Se:impl}

\paragraph{Implementation} Similarly to existing tools like TaintDroid, \Tool\ is implemented as an instrumented version of the Android SDK. Specifically, we have instrumented version 4.1.1\_r6 of the SDK, which was chosen intentionally to match the most recent version of TaintDroid.\footnote{
	\href{http://appanalysis.org/download.html}{http://appanalysis.org/download.html}
} The experimental data we present indeed utilizes TaintDroid for tag propagation (as required for accurate resolution for relevant values).

Beyond the TaintDroid instrumentation scheme, the \Tool\ scheme specifies additional behaviors for sources and sinks within the SDK. At source points, a hook is added to record the private value read by the source statement (which acts as a reference value). At sink points, a hook is installed to apply Bayesian reasoning regarding the legitimacy of the sink.

Analogously to TaintDroid, \Tool\ performs privacy monitoring over APIs for file-system access and manipulation, inter-application and socket communication, reading the phone's state and location, and sending of text messages. \Tool\ also monitors the HTTP interface, camera, microphone, bluetooth and contacts. \OC{As explained in \secref{pseudo}, each of the privacy sources monitored by \Tool\ is mirrored by a tag/feature. The full list of features is as follows: \emph{IMEI}, \emph{IMSI}, \emph{AndroidID}, \emph{Location}, \emph{Microphone}, \emph{Bluetooth}, \emph{Camera}, \emph{Contacts}, \emph{FileSystem}.}

The \Tool\ implementation is configurable, enabling the user to switch between distance metrics as well as enable/disable information-flow tracking for precise/heuristic determination of relevant values. (See \secref{points}.) In our experiments, we tried both the Levenshtein and the Hamming metrics, but found no observable differences, and so we report the results only once. Our reasoning for why the metrics are indistinguishable is because we apply both to equal-length strings (see \secref{similarstr}), and have made sure to apply the same metric both offline and online, and so both metrics achieve a very similar effect in the Bayesian setting.

\paragraph{Training} To instantiate \Tool\ with the required estimates, as explained in \secref{estprob}, we applied the following methodology:
%
First, to estimate $\Pr(\emph{legitimate})$, we relied on (i) an extensive study by Hornyack et al. spanning 1,100 top-popular free Android apps~\cite{HHJSW:CCS11}, as well as (ii) a similarly comprehensive study by Enck et al.~\cite{EOMC:SEC11}, which also spans a set of 1,100 free apps. According to the data presented in these studies, approximately one out of three release points is illegitimate, and thus $\widehat{\Pr}(\emph{legitimate})=0.66$ and complementarily
$\widehat{\Pr}(\emph{illegitimate}) = 1-0.66 \approx 0.33$.

For the conditional probabilities $\widehat{\Pr}(X_i = x_{ij} | Y=y_k)$,  we queried Google Play for the 100 most popular apps (across all domains) in the geography of one of the authors. We then selected at random 35 of these apps, and analyzed their information-release behavior using debug breakpoints
(which we inserted via the {\tt adb} tool that is distributed as part of the Android SDK).

Illegitimate leaks that we detected offline mainly involved (i) location information and (ii) device and user identifiers, which is consistent with the findings reported by past studies~\cite{HHJSW:CCS11,EOMC:SEC11}. We confirmed that illegitimate leaks are largely correlated with high similarity between private data and sink arguments, and so we fixed six distance levels for each private item: $[0,4]$ and ``$\geq 5$''. (See \secref{featext}.) Finally, to avoid zero estimates for conditional probabilities while also minimizing data perturbation, we set the ``smoothing'' factor $l$ in \equref{smoothEstimate} at 1, where the illegitimate flows we detected were in the order of several dozens per private item.

\subsection{Experimental Hypotheses}

%We conducted all of our experiments on clean virtual-machine images with 4GB of RAM running version 12.04.2 LTS of the Ubuntu Linux distribution. For our experiments, we used the Android mobile device emulator included with the Android SDK. We loaded the TaintDroid and \Tool\ images into separate emulators running on different clones of the virtual machine. For TaintDroid, we followed the installation and setup steps provided online.

In our experimental evaluation of \Tool, we tested two hypotheses:
\begin{compactenum}
\item \underline{H1: Accuracy.}
    Bayesian reasoning \JCO{}{about the legitimacy of information release}, as implemented in \Tool,
     yields a significant improvement in leakage-detection accuracy compared to the baseline of information-flow tracking.
\item \underline{H2: Applicability.} For real-life applications, \Tool\ remains effective under relaxation of the 
     tag-based method for detection of relevant values and its stability improves.
\end{compactenum}

\input{exp1}
\input{exp2}




%In the following, we discuss the accuracy, coverage and robustness trends that emerge from \tableref{realworld}.
%
%\paragraph{Accuracy} First, \Tool\ produces more complete results, triggering $>$x2.5 more alarms (21 vs 8) on $>$x2 of the benchmarks (15 vs 7) when restricted to the APIs supported by TaintDroid, and $>$x8 alarms (65 vs 8) on $\sim$x4 of the benchmarks (26 vs 7) in general. The results by both tools are highly precise. We identified only one false alarm --- by \Tool --- due to overlap between benign values: extra information on the {\tt Location} object returned by a call to {\tt LocationManager.getLastKnownLocation(...)} and unrelated metadata passed into a {\tt ContextWrapper.startService(...)} request.
%
%There are no findings reported by TaintDroid that \Tool\ fails to detect. There are, however, alarms triggered by \Tool\ over source/sink pairs supported by TaintDroid that TaintDroid misses
%(e.g., on {\tt ios7lockscreen}, {\tt fingerprint} and {\tt princesshs}). We invested considerable time investigating into these findings, including decompiling the subject apps. For some of the apps (like {\tt princesshs}), the reason for the misses by TaintDroid appears to be that
%TaintDroid limits loading of third-party libraries, and thus certain functionality is not executed, also leading to exceptional app states, which both inhibit certain data leaks.\footnote{
%	See \href{https://groups.google.com/forum/\#!topic/android-security-discuss/U1fteEX26bk}{forum comment} on this by William Enck, the TaintDroid moderator.
%} As for the remaining apps, these all leak data via the {\tt mobileCore} module,\footnote{
%\href{https://www.mobilecore.com/sdk/}{https://www.mobilecore.com/sdk/}
%} which is a highly optimized and obfuscated library, and so a plausible explanation for the misses is that data flow breaks within this library, though we could not confirm this.
%
%A pleasing property of the data-centric approach, especially in comparison with taint analysis, is that it can record not only true alarms but also candidate leakages falling below the designated similarity threshold. We thus went through an extended log of our system, containing also suppressed alarms, and confirmed that all the source/sink pairs that the system resolved not to report were indeed benign.
%
%\paragraph{Coverage} Our second observation is that the TaintDroid APIs are insufficient. The additional internet, system-settings and file-system APIs monitored by our system disclose many more data leaks. We expect that extending TaintDroid to include these additional APIs while retaining the same level of precision would not be easy. (See section 8 in \cite{EGCCJMS:OSDI10}.) We also anticipate observable impact on the performance of TaintDroid.
%
%\paragraph{Robustness} A final point is that \Tool\ appears more stable than TaintDroid, crashing on 8 of the 54 applications, which are a strict --- and small --- subset of the 21 apps TaintDroid crashes on. \Tool\ crashes all stem from missing libraries and/or hardware capabilities in the emulated environment. We conjecture that additional TaintDroid crashes are due to (i) TaintDroid restrictions on loading of third-party libraries, as well as (ii) the intrusive nature of the TaintDroid instrumentation scheme, which reaches into the lowest levels of the Android platform, thereby affecting its stability. This analysis suggests that our approach is more readily applicable to real-world applications.
%
%
%
%
%The tainting approach has been investigated, and shown to be feasible, across multiple studies. A notable implementation of the tainting approach is the TaintDroid system~\cite{EGCCJMS:OSDI10}. TaintDroid is the product of careful engineering, balancing between precision and performance to achieve admissible runtime overhead (mostly below 10\%). TaintDroid tracks taint labels across a select set of sources and sinks. It supports system-wide analysis by tainting files and interprocess messages. TaintDroid has been extended by, and used in, multiple recent studies~\cite{JHW:SPSM12,RCE:CODAPSY13,SPKS:WISTP12}.
